This project presents a comprehensive pipeline for phishing detection using a neural network-based approach. The implementation integrates data preprocessing, a modular custom dataset class, and a feedforward neural network tailored for binary classification. The system is trained on preprocessed phishing data and evaluated for its loss reduction during the training process. This modular approach ensures scalability and serves as a foundation for further exploration in phishing detection and related domains.

Through this project, several lessons were learned. First, effective data preprocessing, such as feature scaling and proper data splitting, is crucial for ensuring consistent model performance. Second, modular design simplifies experimentation and debugging, particularly when integrating new components or modifying existing ones. Additionally, the choice of activation functions and network architecture significantly impacts the model's capacity to generalize. An important lesson from the current implementation is the need for flexible evaluation metrics beyond loss, such as accuracy and F1-score, to fully assess the model's effectiveness.

For future work, several extensions are planned. Incorporating advanced feature engineering techniques, such as leveraging domain-specific knowledge for phishing detection, could improve model accuracy. Exploring more sophisticated neural network architectures, such as convolutional or recurrent layers, might better capture complex patterns in the data. Furthermore, implementing cross-validation and hyperparameter optimization techniques will enhance the model's resilience.

In conclusion, the project establishes a strong baseline for phishing detection while identifying key areas for enhancement. These insights will guide future research and development efforts in phishing detection and cybersecurity applications.

